Meta-analysis

### 2019-11-07 05_MetaAnalysis.Rmd
attempting rma.mv analysis

anova(m8,m9) # 65 has a lower AIC but not evaluated as a significantly better model

@@

>>>>

m10 <- lmer(log(grain_yield.t.ha*1000) ~ (factor(spray_management) | trial_ref), 
           data = slimer_PM_dat)

anova(m8,m9) # m9 is significantly better model
anova(m9,m10) # m9 is significantly better model

@@

```{r}
library(metafor)

slimer_PM_dat <- slimer_PM_dat[!is.na(slimer_PM_dat$yield_error),]
slimer_PM_dat$yi <- log(slimer_PM_dat$grain_yield.t.ha*1000)
slimer_PM_dat$spray_management

PM_mv_AI <- rma.mv(yi,yield_error,
                   mods = spray_management,
                   method = "ML",
                   random = list(~ spray_management | trial_ref),
                   struct = "UN",
                   data = slimer_PM_dat)

PM_mv_AI

anova(PM_mv_AI, L = rbind(c(0,1,-1,0,0), 
                          c(0,0,-1,1,0),
                          c(0,0,-1,0,1),
                          c(0,0,0,-1,1)))
